Security is an important concern among several in modern computer systems. These
concerns often exist in contention over a set of finite resources, e.g. DRAM
bandwidth/capacity, CPU time, drive space. These creating a space of possible
tradeoffs between concerns that allow us to optimize against some constraint.
This research focuses on exploring these disparate tradeoff spaces, specifically
where compromises between service-level security guarantees, system energy
budget, and overall system performance might be made in the interest of
high-performance or low-energy configurations.  these tradeoffs in the context
of drive encryption and file systems is not straightforward.

Full-drive encryption (FDE) is especially important for mobile devices because
they contain large quantities of sensitive data yet are easily lost or stolen.
Unfortunately, the standard approach to FDE---the AES block cipher in XTS
mode---is 3--5x slower than unencrypted storage. Authenticated encryption based
on stream ciphers is already used as a faster alternative to AES in other
contexts, such as HTTPS, but the conventional wisdom is that stream ciphers are
unsuitable for FDE. Used naively in drive encryption, stream ciphers are
vulnerable to attacks, and mitigating these attacks with on-drive metadata is
generally believed to ruin performance.

In this paper, we argue that recent developments in mobile hardware invalidate
this assumption, making it possible to use fast stream ciphers for FDE. Modern
mobile devices employ solid-state storage with Flash Translation Layers (FTL),
which operate similarly to Log-structured File Systems (LFS). They also include
trusted hardware such as Trusted Execution Environments (TEEs) and secure
storage areas. Leveraging these two trends, we propose StrongBox, a stream
cipher-based FDE layer that is a drop-in replacement for dm-crypt, the standard
Linux FDE module based on AES-XTS. StrongBox introduces a system design and
on-drive data structures that exploit LFS's lack of overwrites to avoid costly
rekeying and a counter stored in trusted hardware to protect against attacks. We
implement StrongBox on an ARM big.LITTLE mobile processor and test its
performance under multiple popular production LFSes. We find that StrongBox
improves read performance by as much as $2.36\times$ ($1.72\times$ on average)
while offering stronger integrity guarantees.

Full-drive encryption is especially important for mobile devices because they
contain large quantities of sensitive data yet are easily lost or stolen. As
this research demonstrates, the standard approach to FDE—the AES block cipher in
XTS mode—is 3-5x slower than unencrypted storage. Authenticated encryption based
on stream ciphers is already used as a faster alternative to AES in other
contexts, such as HTTPS, but the conventional wisdom is that stream ciphers are
unsuitable for FDE. Used naively in drive encryption, stream ciphers are
vulnerable to attacks, and mitigating these attacks with on-drive metadata is
generally believed to ruin performance.

With this research, we argue that recent developments in mobile hardware
invalidate this assumption, making it possible to use fast stream ciphers for
FDE. Modern mobile devices employ solid-state storage with Flash Translation
Layers (FTL), which operate similarly to Log-structured File Systems (LFS). They
also include trusted hardware such as Trusted Execution Environments (TEEs) and
secure storage areas. Leveraging these two trends, we proposed a stream
cipher-based FDE layer that is a drop-in replacement for dm-crypt, the standard
Linux FDE module based on AES-XTS.
